---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# eiopaR

<!-- badges: start -->
 [![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://lifecycle.r-lib.org/articles/stages.html#maturing)
 [![R-CMD-check](https://github.com/MehdiChelh/eiopaR/actions/workflows/check-standard.yaml/badge.svg)](https://github.com/MehdiChelh/eiopaR/actions/workflows/check-standard.yaml)
 `r badger::badge_cran_release(NULL, "green")`
<!-- badges: end -->

A simple package to get the EIOPA rates directly in your script.

The data is accessed through an API which is regularly updated with the latest EIOPA rates.

**Note:**

- This package requires an internet connection in order to access the risk-free rates data.
- The API or the [author](mailto:mehdi.echel@gmail.com) of this package are not related to EIOPA.

## Installation

You can install the released version of eiopaR from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("eiopaR")
```

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("MehdiChelh/eiopaR")
```

**Note:** If you use Excel, you can also use the add-in [EIOPA_API.xlam](https://github.com/MehdiChelh/eiopaR/raw/master/EIOPA_API.xlam) of this repository (in the Excel ribbon: `Developer > Add-ins > Browse > EIOPA_API.xlam`). It imports a formula called `EIOPA` that can be used in Excel as follows: `EIOPA("with_va", "FR", 2019, 12)` or also `EIOPA("no_va", "FR", 2019, 12)`.

## Example

The following script gives you the risk-free rates with volatility adjustment:

```{r get_data}
library(eiopaR)

rfr <- get_rfr_with_va(region = "FR", year = 2017:2018, month = 12)
rfr
```

**Note:** It is recommended to **limit the number of calls** to the functions `get_rfr`, `get_rfr_with_va`, `get_rfr_no_va` and to store the results of your calls in the environment variables of your session (like in the example above `rfr <- get_...`). Your IP can be temporary or permanently blocked if too many queries are executed.

The rates are then accessible as a `data.frame`:

```{r show_data}
head(rfr$data)
```


```{r plot_data, out.width="65%", fig.align = 'center'}
plot(
  rfr$data$`20171231_rfr_spot_with_va_FR`,
  ylab = "2017-12",
  type = 'l',
  col = "purple"
)
```


## Contributing
Pull requests are welcome. For major changes, please open an issue first to discuss what you would like to change.

Please make sure to update tests as appropriate.

## Credit
See [EIOPA | Risk-free interest rate term structures](https://www.eiopa.europa.eu/tools-and-data/risk-free-interest-rate-term-structures_en) for more information.

## License
[MIT](https://choosealicense.com/licenses/mit/)

